\documentclass[a4paper,12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{a4paper, total={170mm,257mm}, left=20mm, top=20mm}

\title{\textbf{Rust Developer}}
\author{Alexey Leonidovich Belyakov}

\begin{document}

\maketitle

\begin{center}
    \begin{tabular}{rl}
        \textbf{Phone:} & +7 (911) 261-70-72 \\
        \textbf{Telegram:} & \href{https://leqqrm.t.me}{leqqrm.t.me} \\
        \textbf{Email:} & \href{mailto:qqrm@vivaldi.net}{qqrm@vivaldi.net} \\
        \textbf{GitHub:} & \href{https://github.com/qqrm}{github.com/qqrm} \\
    \end{tabular}
\end{center}

\section*{Languages}
\begin{itemize}
    \item Russian — Native
    \item English — Advanced (B2)
\end{itemize}

\section*{Objective}
Highly skilled and experienced Lead Rust Developer with nearly a decade of experience in software development and system architecture. Committed to pushing the boundaries of software engineering, aiming to contribute to cutting-edge projects, and drive excellence in development practices. Eager to lead and inspire teams, solve complex challenges, and create robust software systems that impact the technology landscape.

\section*{Work Experience}

\subsection*{Lead Rust Developer @ YADRO}
\textbf{March 2023 — Present}
\begin{itemize}
    \item Designed the architecture of a hardware-software complex for deduplication-based backup solutions.
    \item Conducted research on optimizing RocksDB and enhancing NVMe disk performance.
    \item Implemented data structures for efficient storage of hashes and hash-hashes.
    \item Resolved bugs and improved compression and deduplication modules.
    \item Conducted code reviews and delivered internal lectures on Rust, facilitating the transition of ex-C++ developers to idiomatic Rust.
\end{itemize}

\subsection*{Senior Rust/Python Developer (Part-Time) @ Ultima-bi}
\textbf{November 2022 - March 2023 (5 months)}
\begin{itemize}
    \item Developed Python wrappers and caching systems for data science tools based on Polars.
\end{itemize}

\subsection*{Rust Team Lead @ Solcery}
\textbf{March 2022 — March 2023 (1 year)}
\begin{itemize}
    \item Developed a blockchain-based database using Solana smart contracts, focusing on DAO and card game frameworks.
    \item Managed low-level data storage structures, versioning, and table migrations.
    \item Acted as the bridge between technical and business aspects, formulated requirements, and architected solutions.
\end{itemize}

\subsection*{Senior Rust Developer @ Kaspersky Lab}
\textbf{May 2021 — March 2022 (11 months)}
\begin{itemize}
    \item Developed and maintained a blockchain-based voting service using Exonum.
    \item Expanded integration and unit testing for existing functionality.
    \item Added weight-based functionality to the voting system.
    \item Refactored the codebase and facilitated the migration to the Microsoft ecosystem.
\end{itemize}

\subsection*{Rust Developer @ Kryptonite}
\textbf{May 2020 — May 2021 (1 year 1 month)}
\begin{itemize}
    \item Ported a voice call processing system (originally written in Scala) to Rust.
    \item Implemented functionality for voice recording normalization and conversion to embeddings.
    \item Developed a module for synchronizing dialogues from different audio tracks.
    \item Designed a module to store decrypted dialogues in a database.
    \item Created rigorous unit test suites to validate and ensure the reliability of new features.
\end{itemize}

\subsection*{Senior C++/Go Developer @ B2Broker}
\textbf{November 2018 — March 2020 (1 year 6 months)}
\begin{itemize}
    \item Developed financial software using MT4 and MT5 API.
    \item Developed a trade copier for MT4 and MT5 platforms.
    \item Created a Multi Account Manager for fund delegation and reward calculation.
    \item Designed and implemented microservices for data normalization and delivery from MT4 and MT5 to widgets.
    \item Established data collectors for statistical analysis.
\end{itemize}

\subsection*{Middle->Senior C++ Developer @ ASCON}
\textbf{May 2016 — November 2018 (2 years 7 months)}
\begin{itemize}
    \item Contributed to the development of libraries for architectural design of construction objects and technical communications.
    \item Added a "Change View Plane" feature.
    \item Designed and implemented a framework for automated testing.
    \item Participated in a major codebase refactoring, including transitioning to C++17.
    \item Upgraded to a new GUI version in KOMPAS V17.
    \item Introduced Git, Slack, and integration tests.
\end{itemize}

\subsection*{Middle C++ Developer @ Con Certeza}
\textbf{March 2015 — April 2016 (1 year 2 months)}
\begin{itemize}
    \item Developed a sniffer and parser for signaling traffic (comprising the entire SS7 protocol stack) for the SORM system for MTS.
    \item Authored parsers for protocols such as INAP, RANAP, MAP, TCAP, CAP, MTP3, MTP2, SCCP, and SIP.
    \item Designed and implemented modules to gather information from traffic based on RFC protocols for SMS, subscriber movements, and telephone calls.
    \item Created integration tests for the implemented functionality using Python.
\end{itemize}

\subsection*{Middle C++/JS Developer @ LiveTex}
\textbf{July 2014 — March 2015 (7 months)}
\begin{itemize}
    \item Created wrapper modules for PostgreSQL and ZeroMQ for Node.js.
\end{itemize}

\subsection*{Junior C++ Developer @ Tools for Brokers}
\textbf{November 2013 — July 2014 (9 months)}
\begin{itemize}
    \item Developed for the MetaTrader 4 and 5 platforms.
    \item Enhanced and debugged a plug-in for mutual fund investments (UMAM).
    \item Built a web application for MT4 server management.
\end{itemize}

\end{document}
